Robust Estimation, Prediction and Control with \\ Linear Dynamics and Arbitrary Costs

### 2020-01-14 main.tex
Confidence ellipsoid proof complete

	\twocolumn[
	\icmltitle{Robust Estimation, Prediction and Control with \\ Continuous States and Dynamics Structure}

@@

Denote $\eta(t) = C\nu(t) + D\omega(t)$. By substituting the expression of $y_n$ into \eqref{eq:vector_rls}, we obtain:
\begin{lemma}[Regression error]
\label{lem:regression-error}
\begin{align*}
    \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - \lambda G_{N, \lambda}^{-1}\theta 
\end{align*}
\end{lemma}

Depending on the assumption we take over the noise $\eta_n$ and the true parameter $\theta$, we can bound the regression error $\theta_{N,\lambda} - \theta$ in different ways.

@@

Then, 
\begin{align}
\|\theta_{N,\lambda} - \theta\|_1 \leq &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
&+ \lambda\|G_{N, \lambda}^{-1}\|_1\|\theta\|_\infty \nonumber
\end{align}

@@

If \autoref{assumpt:bounded-noise} does not hold, another weaker assumption can be made.

@@

\begin{assumption}[Sub-Gaussian Noise Model]
\label{assumpt:gaussian-noise}
At each time $t\geq0$ the sum $\eta(t)$ of projected measurement noise $\nu(t)$ and disturbance $\omega(t)$ is a sub-Gaussian noise with covariance proxy $\Sigma_p \in \Real^{p\times p}$:
\begin{equation*}
    \eta(t) = C\nu(t) + D\omega(t) \sim Sub_G(\Sigma_p).
\end{equation*}
For instance, this is the case of $\nu$ and $\omega$ are Gaussian noises with respective covariance matrices $\Sigma_r$ and $\Sigma_s$, with $\Sigma_p \eqdef C\Sigma_r C^\transp + D\Sigma_s D^\transp$. Also note that \autoref{assumpt:bounded-noise} implies that $\eta$ is $\|\eta\|_\infty I_p$-sub-Gaussian, and is therefore a stronger assumption.
\end{assumption}

\begin{proposition}[Theorem 1 of \citep{Abbasi2011}, Matrix version]
\label{prop:concentration}
Let $\{F_t\}_{t=0}$ be a filtration.
Let $\{\eta_t\}_{t=1}^\infty$ be a $\Real^p$-valued stochastic process such that $\eta_t$ is $F_t$-measurable and $\expectedvalue\left[\eta_t\condbar F_{t-1}\right]$ is $\Sigma_p$-sub-Gaussian.

Let $\{\Phi_t\}_{t=1}^\infty$ be an $\Real^{p\times d}$-valued stochastic process such that $\Phi_t$ is $F_t$-measurable. Assume that $G$ is a $d\times d$ positive definite matrix. For any $t\geq 0$, define:
\begin{equation*}
    \overline{G}_t = G + \sum_{s=1}^t \Phi_s^\transp \Sigma_p^{-1} \Phi_s \in \Real^{d\times d} \quad S_t = \sum_{s=1}^t \Phi_s^\transp\Sigma_p^{-1}\eta_s \in \Real^{d}.
\end{equation*}
Then, for any $\delta>0$, with probability at least $1-\delta$, for all $t\geq0$,
\begin{align*}
\| S_t \|_{\overline{G}_t^{-1}} \geq \sqrt{2\ln \left(\frac{\det\left(\overline{G}_t\right)^{1/2}}{\delta\det(G)^{1/2}}\right)}.
\end{align*}
\end{proposition}

\begin{theorem}[Confidence ellipsoid]
\label{thm:confidence_ellipsoid}

@@

\begin{lemma}[Confidence polytope]
\label{lem:confidence_polytope}
We can enclose the confidence ellipsoid $C_\delta$ obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $P_\delta$:
\[\cC_\delta \subset \cP_\delta\]
where $\cP_\delta$ can be written as:
\begin{equation}
     \cP_\delta = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
\end{equation}
with 
\begin{align*}
    &G_{N,\lambda}^{-1} = PDP^{-1}\\
    &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{, for } k\in[2^d]\\
    &\Delta\theta_k = C_{N,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k \\
    &A_0 = \theta_{N,\lambda}^\transp\Phi\\
    &\Delta A_k = \Delta\theta_k^\transp\Phi\\
\end{align*}
This conversion is illustrated in \autoref{fig:ellipsoid_to_polytope}
\end{lemma}

@@

In order to use the interval predictor from \citep{leurent2019interval}, we also require $A_0$ to be Metzler. This can be ensured under some conditions:

\begin{lemma}[Similarity transformation \citep{Efimov_a2013}]
\label{lem:metzler} Let $D\in\Xi\subset\Real^{n\times n}$ be a matrix variable satisfying the interval constraints $\Xi=\{D\in\Real^{n\times n}:\,D_{a}-\Delta\le D\le D_{a}+\Delta\}$ for some $D_{a}^{\text{T}}=D_{a}\in\Real^{n\times n}$ and $\Delta\in\Real_{+}^{n\times n}$. If for some constant $\mu\in\Real_{+}$ and a diagonal matrix $\Upsilon\in\Real^{n\times n}$ the Metzler matrix $Y=\mu E_{n\times n}-\Upsilon$ has the same eigenvalues as the matrix $D_{a}$, then there is an orthogonal matrix $S\in\Real^{n\times n}$ such that the matrices $S^{\text{T}}DS$ are Metzler for all $D\in\Xi$ provided that $\mu>n||\Delta||_{max}$.\textup{ }
\end{lemma}

\begin{theorem}[Interval Predictor \citep{leurent2019interval}]
\label{thm:predictor}
Assuming that \eqref{eq:polytope} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
\begin{eqnarray}
\dot{\underline{x}}(t) & = & A_{0}\underline{x}(t)-\Delta A_{+}\underline{x}^{-}(t)-\Delta A_{-}\overline{x}^{+}(t)\nonumber \\
 &  & +Bu(t)+D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\nonumber\\
\dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t) \label{eq:interval_predictor} \\
 &  & +Bu(t)+D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
 &  & \underline{x}(0)=\underline{x}_{0},\;\overline{x}(0)=\overline{x}_{0}\nonumber 
\end{eqnarray}
ensures the inclusion property \eqref{eq:interval_property}. If there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
\begin{gather*}
P+\min\{Z_{+},Z_{-}\}>0,\;\Upsilon\preceq0,\;\Gamma>0,\\
Q+\min\{Q_{+},Q_{-}\}+2\min\{\Psi_{+},\Psi_{-}\}>0,
\end{gather*}
where{\footnotesize{}
\begin{gather*}
\Upsilon=\left[\begin{array}{cccc}
\Upsilon_{11} & \Upsilon_{12} & \Upsilon_{13} & P\\
\Upsilon_{12}^{\top} & \Upsilon_{22} & \Upsilon_{23} & Z_{+}\\
\Upsilon_{13}^{\top} & \Upsilon_{23}^{\top} & \Upsilon_{33} & Z_{-}\\
P & Z_{+} & Z_{-} & -\Gamma
\end{array}\right],\\
\Upsilon_{11}=\mathcal{A}^{\top}P+P\mathcal{A}+Q,\;\Upsilon_{12}=\mathcal{A}^{\top}Z_{+}+PR_{+}+\Psi_{+},\\
\Upsilon_{13}=\mathcal{A}^{\top}Z_{-}+PR_{-}+\Psi_{-},\;\Upsilon_{22}=Z_{+}R_{+}+R_{+}^{\top}Z_{+}+Q_{+},\\
\Upsilon_{23}=Z_{+}R_{-}+R_{+}^{\top}Z_{-}+\Psi,\;\Upsilon_{33}=Z_{-}R_{-}+R_{-}^{\top}Z_{-}+Q_{-},\\
\mathcal{A}=\left[\begin{array}{cc}
A_{0} & 0\\
0 & A_{0}
\end{array}\right],\;R_{+}=\left[\begin{array}{cc}
0 & -\Delta A_{-}\\
0 & \Delta A_{+}
\end{array}\right],\;R_{-}=\left[\begin{array}{cc}
\Delta A_{+} & 0\\
-\Delta A_{-} & 0
\end{array}\right],
\end{gather*}
}then the predictor \eqref{eq:interval_predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
\end{theorem}

@@

\begin{equation}
\hat{v}^r(\bu) \eqdef \sum_{t=0}^\infty \gamma^t \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]}  r(x)
\end{equation}
where $\underline{x}(t, \bu), \overline{x}(t, \bu)$ follow the dynamics defined in \eqref{eq:interval_predictor}.
\end{definition}

@@

If we assume that $R$ is $L$-Lipschitz, then we can bound the other side:
\begin{equation*}
     \hat{v}^r(\bu) \leq v^r(\bu) \leq \hat{v}^r(\bu) + L\sum_{t=0}^\infty \gamma^t \mu([\underline{x}_N(t),\overline{x}_N(t)])
\end{equation*}
\end{proposition}

@@

\section{The Use-Case of Autonomous Driving}

@@

In the following, we describe the system and its associated interval predictor.

@@

\appendix

\subsection{Proof of \autoref{lem:regression-error}}

\begin{proof}
In order to study the concentration of $\theta_{N,\lambda}$, we substitute the expression of $y_n$ into \eqref{eq:vector_rls}:
\begin{align*}
    \theta_{N,\lambda} &= G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} (\Phi_n\theta +\eta_n)\\
    &= \theta - G_{N, \lambda}^{-1}\lambda\theta + G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n
\end{align*}

Next, we consider the stopped martingale $M_{\min(\tau,t)}^z$. Since 
$(M_t^z)_{t=1}^\infty$ is a non-negative supermartingale and $\tau$ is a random stopping time, we deduce by Doob's decomposition that
\begin{align*}
\expectedvalue[M_{\min(\tau,t)}^z] &= \expectedvalue[M_0^z] + \expectedvalue[\sum_{s=0}^{t-1} (M_{s+1}^z-M_s^z) \mathbb{I}\{\tau>s\}]\\
&\leq 1 + \expectedvalue[\sum_{s=0}^{t-1} \expectedvalue[M_{s+1}^z-M_s^z|F_{s}] \mathbb{I}\{\tau>s\}]\\
&\leq 1
\end{align*}
Finally, an application of Fatou's lemma show that 
$\expectedvalue[M_\tau^z] = \expectedvalue[\liminf_{t\to\infty} M_{\min(\tau,t)}^z] \leq \liminf_{t\to\infty} \expectedvalue[M_{\min(\tau,t)}^z] \leq 1.$
\end{proof}

By applying \autoref{prop:concentration}, we obtain:
\begin{align*}
    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq 
     + \lambda\|\theta\|_{G_{N, \lambda}^{-1}}
\end{align*}
\end{proof}

>>>>

	\twocolumn[
	\icmltitle{Robust Estimation, Prediction and Control with \\ Linear Dynamics and Arbitrary Costs}

@@

Denote $\eta(t) = C\nu(t) + D\omega(t)$. By simply substituting the expression of $y_n$ into \eqref{eq:vector_rls}, we obtain the regression error:
\begin{align}
    \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - \lambda G_{N, \lambda}^{-1}\theta 
\end{align}

Depending on the assumption we have over the noise $\eta_n$ and the true parameter $\theta$, we can bound this error in different ways.

@@

Then, 
\begin{align}
\label{eq:bounded-noise-polytope}
\|\theta_{N,\lambda} - \theta\|_1 \leq &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
&+ \lambda\|G_{N, \lambda}^{-1}\|_1\|\theta\|_\infty \nonumber
\end{align}

@@

There may be cases where \autoref{assumpt:bounded-noise} does not hold, for instance if the noise $\eta$ is Gaussian, which implies $\|\eta\|_\infty=+\infty$ and makes \eqref{eq:bounded-noise-polytope} uninformative. Then, another weaker assumption can be made.

@@

\begin{assumption}[Sub-Gaussian Noise]
\label{assumpt:gaussian-noise}
At each time $t\geq0$ the noise $\eta(t)$ is an independent sub-Gaussian noise with covariance proxy $\Sigma_p \in \Real^{p\times p}$:
\begin{equation*}
    \eta(t) \sim Sub_G(\Sigma_p).
\end{equation*}
For instance, this is the case when $\nu$ and $\omega$ are Gaussian noises with respective covariance matrices $\Sigma_r$ and $\Sigma_s$, with $\Sigma_p \eqdef C\Sigma_r C^\transp + D\Sigma_s D^\transp$. Also note that \autoref{assumpt:bounded-noise} implies that $\eta$ is $\|\eta\|_\infty I_p$-sub-Gaussian, and is therefore a stronger assumption.
\end{assumption}

\begin{proposition}[Theorem 1 of \citep{Abbasi2011}, Matrix version]
\label{prop:concentration}
Let $\{F_n\}_{n=0}$ be a filtration.
Let $\{\eta_n\}_{n=1}^\infty$ be a $\Real^p$-valued stochastic process such that $\eta_n$ is $F_n$-measurable and $\expectedvalue\left[\eta_n\condbar F_{n-1}\right]$ is $\Sigma_p$-sub-Gaussian.

Let $\{\Phi_n\}_{n=1}^\infty$ be an $\Real^{p\times d}$-valued stochastic process such that $\Phi_n$ is $F_n$-measurable. Assume that $G$ is a $d\times d$ positive definite matrix. For any $n\geq 0$, define:
\begin{equation*}
    \overline{G}_n = G + \sum_{s=1}^n \Phi_s^\transp \Sigma_p^{-1} \Phi_s \in \Real^{d\times d} \quad S_n = \sum_{s=1}^n \Phi_s^\transp\Sigma_p^{-1}\eta_s \in \Real^{d}.
\end{equation*}
Then, for any $\delta>0$, with probability at least $1-\delta$, for all $n\geq0$,
\begin{align*}
\| S_n \|_{\overline{G}_n^{-1}} \geq \sqrt{2\ln \left(\frac{\det\left(\overline{G}_n\right)^{1/2}}{\delta\det(G)^{1/2}}\right)}.
\end{align*}
\end{proposition}

\begin{theorem}[Confidence ellipsoid]
Under \autoref{assumpt:gaussian-noise}, it holds with probability at least $1-\delta$ that
\begin{align}
    \label{eq:confidence-ellipsoid}
    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
     + \lambda^{1/2}\|\theta\|_2.
\end{align}
\label{thm:confidence_ellipsoid}

@@

\begin{lemma}[Confidence polytope]
\label{lem:confidence_polytope}
We can enclose the confidence ellipsoid $C_\delta$ obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $P_\delta$:
\[\cC_\delta \subset \cP_\delta\]
where $\cP_\delta$ can be written as:
\begin{equation}
     \cP_\delta = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
\end{equation}
with 
\begin{align*}
    &G_{N,\lambda}^{-1} = PDP^{-1}\\
    &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{, for } k\in[2^d]\\
    &\Delta\theta_k = C_{N,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k \\
    &A_0 = \theta_{N,\lambda}^\transp\Phi\\
    &\Delta A_k = \Delta\theta_k^\transp\Phi
\end{align*}
This conversion is illustrated in \autoref{fig:ellipsoid_to_polytope}.
\end{lemma}

@@

In order to use the interval predictor from \citep{leurent2019interval}, we need an additional assumption.

% \begin{lemma}[Similarity Transformation]
% \label{lem:metzler} Let $D\in\Xi\subset\Real^{n\times n}$ be a matrix variable satisfying the interval constraints $\Xi=\{D\in\Real^{n\times n}:\,D_{a}-\Delta\le D\le D_{a}+\Delta\}$ for some $D_{a}^{\text{T}}=D_{a}\in\Real^{n\times n}$ and $\Delta\in\Real_{+}^{n\times n}$. If for some constant $\mu\in\Real_{+}$ and a diagonal matrix $\Upsilon\in\Real^{n\times n}$ the Metzler matrix $Y=\mu E_{n\times n}-\Upsilon$ has the same eigenvalues as the matrix $D_{a}$, then there is an orthogonal matrix $S\in\Real^{n\times n}$ such that the matrices $S^{\text{T}}DS$ are Metzler for all $D\in\Xi$ provided that $\mu>n||\Delta||_{max}$.\textup{ }
% \end{lemma}

\begin{assumption}
There exists an orthogonal $S\in\Real^{d\times d}$ such that $S^\transp A_0 S$ is Metzler.
\end{assumption}

This for instance the case when $A_0$ is diagonalizable. Another way ... the similarity transformation of \citep{Efimov_a2013}.

\begin{theorem}[Interval Predictor \citep{leurent2019interval}]
\label{thm:predictor}
Assuming that \eqref{eq:polytope} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
\begin{eqnarray}
\dot{\underline{x}}(t) & = & A_{0}\underline{x}(t)-\Delta A_{+}\underline{x}^{-}(t)-\Delta A_{-}\overline{x}^{+}(t)\nonumber \\
 &  & +Bu(t)+D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\nonumber\\
\dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t) \label{eq:interval_predictor} \\
 &  & +Bu(t)+D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
 &  & \underline{x}(0)=\underline{x}_{0},\;\overline{x}(0)=\overline{x}_{0}\nonumber 
\end{eqnarray}
ensures the inclusion property \eqref{eq:interval_property}.

Moreover, the stability of the predictor can be assessed with a sufficient condition in form of an LMI.
% if there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
% \begin{gather*}
% P+\min\{Z_{+},Z_{-}\}>0,\;\Upsilon\preceq0,\;\Gamma>0,\\
% Q+\min\{Q_{+},Q_{-}\}+2\min\{\Psi_{+},\Psi_{-}\}>0,
% \end{gather*}
% where{\footnotesize{}
% \begin{gather*}
% \Upsilon=\left[\begin{array}{cccc}
% \Upsilon_{11} & \Upsilon_{12} & \Upsilon_{13} & P\\
% \Upsilon_{12}^{\top} & \Upsilon_{22} & \Upsilon_{23} & Z_{+}\\
% \Upsilon_{13}^{\top} & \Upsilon_{23}^{\top} & \Upsilon_{33} & Z_{-}\\
% P & Z_{+} & Z_{-} & -\Gamma
% \end{array}\right],\\
% \Upsilon_{11}=\mathcal{A}^{\top}P+P\mathcal{A}+Q,\;\Upsilon_{12}=\mathcal{A}^{\top}Z_{+}+PR_{+}+\Psi_{+},\\
% \Upsilon_{13}=\mathcal{A}^{\top}Z_{-}+PR_{-}+\Psi_{-},\;\Upsilon_{22}=Z_{+}R_{+}+R_{+}^{\top}Z_{+}+Q_{+},\\
% \Upsilon_{23}=Z_{+}R_{-}+R_{+}^{\top}Z_{-}+\Psi,\;\Upsilon_{33}=Z_{-}R_{-}+R_{-}^{\top}Z_{-}+Q_{-},\\
% \mathcal{A}=\left[\begin{array}{cc}
% A_{0} & 0\\
% 0 & A_{0}
% \end{array}\right],\;R_{+}=\left[\begin{array}{cc}
% 0 & -\Delta A_{-}\\
% 0 & \Delta A_{+}
% \end{array}\right],\;R_{-}=\left[\begin{array}{cc}
% \Delta A_{+} & 0\\
% -\Delta A_{-} & 0
% \end{array}\right],
% \end{gather*}
% }then the predictor \eqref{eq:interval_predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
\end{theorem}

@@

\begin{equation}
\hat{v}^r(\bu) \eqdef \sum_{t=0}^\infty \gamma^t \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]}  R(x)
\end{equation}
where $\underline{x}(t, \bu), \overline{x}(t, \bu)$ follow the dynamics defined in \eqref{eq:interval_predictor}.
\end{definition}

@@

If we assume that $R$ is $L$-Lipschitz, then we can also bound the other side:
\begin{equation*}
     \hat{v}^r(\bu) \leq v^r(\bu) \leq \hat{v}^r(\bu) + L\sum_{t=0}^\infty \gamma^t \mu([\underline{x}_N(t),\overline{x}_N(t)])
\end{equation*}
\end{proposition}

@@

\section{Experiments}

@@

The system

\clearpage
\appendix

Next, we consider the stopped martingale $M_{\min(\tau,t)}^z$. Since 
$(M_t^z)_{t=1}^\infty$ is a non-negative supermartingale and $\tau$ is a random stopping time, we deduce by Doob's decomposition that
\begin{align*}
\expectedvalue[M_{\min(\tau,t)}^z] &= \expectedvalue[M_0^z] + \expectedvalue[\sum_{s=0}^{t-1} (M_{s+1}^z-M_s^z) \mathbb{I}\{\tau>s\}]\\
&\leq 1 + \expectedvalue[\sum_{s=0}^{t-1} \expectedvalue[M_{s+1}^z-M_s^z|F_{s}] \mathbb{I}\{\tau>s\}]\\
&\leq 1
\end{align*}
Finally, an application of Fatou's lemma show that 
$\expectedvalue[M_\tau^z] = \expectedvalue[\liminf_{t\to\infty} M_{\min(\tau,t)}^z] \leq \liminf_{t\to\infty} \expectedvalue[M_{\min(\tau,t)}^z] \leq 1.$

By applying \autoref{prop:concentration} with $G=\lambda I_d$, we obtain that with probability at least $1-\delta$,
\begin{align*}
    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
     + \lambda\|\theta\|_{G_{N, \lambda}^{-1}}
\end{align*}
And since $\|\theta\|_{G_{N, \lambda}^{-1}}^2 \leq 1/\lambda_{\min}(G_{N,\lambda})\|\theta\|_2^2 \leq 1/\lambda \|\theta\|_2^2$,
\begin{align*}
    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
     + \lambda^{1/2}\|\theta\|_2
\end{align*}
\end{proof}

\section{The use case of autonomous driving}

In the following, we describe the structure of the model representing the dynamics of of several vehicles driving and interacting with one another.

@@
